Evidence of the necessity of isotopic precise calculation in fuel cycle calculation

### 2016-07-01 paper.tex
first add of FCDP cycle
increase line size for figure, add NEUP logo and Acknowledgments

\institute{
$^{*}$University of Wisconsin-Madison, WI
\and
%$^{\dagger}$State Capitol Building, Springfield, IL
}

@@

%% PPHW: Can we add the official FCDP images

@@

Because the neural network model allows only to mix a plutonium stream into a
uranium stream, slight modification have been made on the cycle: in both ``J1''
and ``E3'' streams uranium and plutonium are separated, the uranium and
plutonium sub-streams are mix together to build one stream of pure uranium and
one stream of pure plutonium.

@@

A last calculation, on decay have been performed using the ``Pu-equivalent''
fabrication model, increasing by a factor 2, 5 and 10 the amount of plutonium in
the startup inventory.  This mimics different degrees of a plutonium accumulation,
and thus different impacts from the decay of this plutonium.
This calculation shows a change from 10 to 30\% in the mixing ratio required to
build the proper PWR-MOX fuel. This kind of plutonium accumulation can
unexpectedly occur in a real fuel cycle and might need to be considered in a
complete fuel cycle transition study.
%% PPHW - do you plot results for this?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
Shall we acknowledge anyone ? DOE ? FCO ?

>>>>

\institute{
$^{*}$University of Wisconsin-Madison, WI
}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{FCDP_cycle}
  \caption{Schematic representation of the EG29 fuel cycle taken from \cite{FCDP}.}
  \label{fig:FCDP}
\end{figure}
%% PPHW: Can we add the official FCDP images

@@

Because the neural network model allows only to mix a plutonium stream into a
uranium stream, slight modification have been made on the cycle: in both ``J1''
and ``E3'' streams uranium and plutonium are separated, the uranium and
plutonium sub-streams are mix together to build one stream of pure uranium and
one stream of pure plutonium. That is why, when comparing the different fuel
fabrication models only the total plutonium enrichement are compared.

@@

A last calculation, on decay have been performed using the ``Pu-equivalent''
fabrication model, increasing by a factor 2, 5 and 10 the amount of plutonium in
the startup inventory. This mimics different degrees of a plutonium accumulation,
and thus different impacts from the decay of this plutonium.
This calculation results in a change in the mixing ratio required to build the
PWR-MOX fuel of 10 to 30\%. This kind of plutonium accumulation can
unexpectedly occur in a real fuel cycle and might need to be considered in a
complete fuel cycle transition study.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments} 
This work was funded in part by the Nuclear Energy University Program 
(DE-NE0000673) and Idaho National Laboratory (154956).
\begin{center}
\includegraphics[width=1.5in]{neup_logo_large.jpg}
\end{center}
